\documentclass[14pt, a4paper]{article}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{float}
\setlength{\parindent}{2em}
\begin{document}
	\section{List}
	This is a section containing a sample list.Try to reproduce it.
	\begin{enumerate}
    \item \textsc{First item} 
    \item second item
    \begin{itemize}
        \item nested one
        \item[] special one
        \begin{itemize}
            \item \textit{another level}
            \item \textbf{Ok} enough
        \end{itemize}
    \end{itemize}
    \item another
    \begin{enumerate}
        \item \textbf{what is happening}
        \item[] I am here
        \item[] \textbf{CSE} Computer science and engineering
        \item[] \textbf{ME} Mechanical Engineering
    \end{enumerate}
    Here is some filler texts. hiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiii husisdjdjdid9oide.hiouerewruiowf cghiuywoeriwfoif.
    \end{enumerate}
    \section{Fonts}
    \subsection{Normal fonts}
    These are some normal texts.
    \subsubsection{Color}
    \textcolor{blue}{This is a sample text in blue.blue blue green green yellow red red. Here is some filler texts. hiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiii husisdjdjdid9oide.hiouerewruiowf cghiuywoeriwfoif.}\par
    \textcolor{red}{This is a sample text in blue.blue blue green green yellow red red. Here is some filler texts. hiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiii husisdjdjdid9oide.hiouerewruiowf cghiuywoeriwfoif.}\par
    This is a sample text in blue.blue blue green green yellow red red. Here is some filler texts. hiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiiii husisdjdjdid9oide.hiouerewruiowf cghiuywoeriwfoif.
    \pagebreak
    \section*{Tables}
    Table 1 is very hard.
    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
       \hline
       left  & 2 & 3 & 4 & 5 \\
       \hline
       \multicolumn{2}{c}{This is } & \multicolumn{3}{c}{Tough}\\
       \cline{3-5}
       \multicolumn{2}{c}{difficult } & I & \multicolumn{2}{c|}{What}\\
       \cline{1-3}
       \multicolumn{3}{|c|}{Here I am } & \multicolumn{2}{c|}{is} \\
        \hline
    \end{tabular}
    \caption{ Hardest Table!}
    \end{table}
\end{document}